---

title: "Abalone dataset analysis"
author: "Vital"
date: "August 30, 2017"
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(shiny)
library(ggplot2)
library(caret)
library(C50)
library(randomForest)
abalone <- read.csv("abalone.csv")
abalone <- abalone[,c(2:10)]
listOfNames <- names(abalone)
rest <- listOfNames[c(1,9)]
listOfNames <- listOfNames[2:8]
abaloneGood <- abalone
```

## Main idea:
With this app you can investigate how lm, rf, gbm and c50 works using abalone dataset

       -please choose any columns to add or remove
       -you should use all genders to enter ML tab (classification task)
       -plots will dynamically fit to your needs
       -investigate how outliers affect lm line
       -research how number of predictors builds an outcome
       
---
       
##LM  abalone relationship: number of rings as outcome with shell.wt as predictor

```{r plot1,echo=FALSE}
       
       gg <- ggplot(abalone, aes(shell.wt, rings))
       gg <- gg + geom_jitter(alpha=0.25)
       gg <- gg + geom_smooth(method=loess, se=FALSE)
       gg <- gg + facet_grid(. ~ sex)
       gg

```


---


## ML with only 2 predictors: length and diametter (rf)

```{r plot2,echo=FALSE}
       set.seed(998)
       metric <- "Accuracy"
       tmp <- abalone[,c(1,2,3,9)]
       inTraining <- createDataPartition(tmp$sex, p = .75, list = FALSE)
       training <- tmp[ inTraining,]
       testing  <- tmp[-inTraining,]
       fitControl <- trainControl(## 10-fold CV
              method = "repeatedcv",
              number = 5,
              repeats = 3)
       
       rf <- train(sex ~ ., data = training, 
                                  method="rf", 
                                  trControl = fitControl,
                                  verbose = FALSE,
                                  metric = metric)
       rf
```


---


## Updating number of predictors and precision increases

```{r plot3,echo=FALSE}
       set.seed(777)
       metric <- "Accuracy"
       inTraining <- createDataPartition(abalone$sex, p = .75, list = FALSE)
       training <- abalone[ inTraining,]
       testing  <- abalone[-inTraining,]
       fitControl <- trainControl(## 10-fold CV
              method = "repeatedcv",
              number = 5,
              repeats = 3)
       
       rf <- train(sex ~ ., data = training, 
                                  method="rf", 
                                  trControl = fitControl,
                                  verbose = FALSE,
                                  metric = metric)
       rf

```



